MS Yeo 7 Network Analyses

### 2022-08-01 msdepression/scripts/yeo_7_network_analyses_20220628.Rmd
Yeo networks

---
title: "MS Prelim Data K23"
author: "Erica Baller"
date: "2/25/2022"
output:
  html_document: default
  pdf_document: default
---

@@

## MS preliminary data

Ideas:

Overall:

[] demographics - tables made below

[] imaging parameters

Aim 1: lesion network mapping
[] some picture showing the # of people who are scanned and the # of people with depression. Maybe an adaptation of Syndey's picture somehow. 
[] mimosa picture
[] picture of filtering pipeline
[] comparison of some of the histograms for high volume loss similar to prev literature(CN II, slf), not so much in other areas
[] results of age analysis [maybe/maybe not, to prove the method works]?
[] results of disease in vs outside of depression network (corrected), lead with this?
[] results total proportion lost (single p)
[] results of dep vs controls across all regions,(uncorrected)
[] results of dep vs controls in depression network (uncorrected)

[] prelim network enrichment via spin-testing or just citation?
- do I want to validate here or somewhere else with neurosynth maps?

Aim 2: prospective
[] power analysis
[] CNB (Bart has great Figure 3)
[] Goassess

Aim 3
[] Hydra picture
[] hydra results from my paper
[] acquisition protocol (T1, t2, flair, dwi)

@@

  A note on the "depression network." This network was made by Shan Siddiqi in Michael Fox's group by doing a conglomeration of TMS datasets, stroke datasets, Nature Human Behavior 2021 (https://www.nature.com/articles/s41562-021-01161-1). It is an unthresholded mask (which I think is in Ts per their supplement). To use it, I binarized it, and then used it as an ROI and calculated, per fascicle, the proportion of the volume occupied by the fascicle that intersected with the depression mask to the whole volume of the fascicle. Most fascicles were either entirely overlapping or entirely outside the depression mask. We consider the fascicles that had any intersection with the binary depression mask to be within the depression mask, or "indepnet." 47 out of 87 fascicles are in this network. We have an even tighter mask "indepnet_10percent", which indicates that at least 10% of a fascicle's volume intersected or overlapped with the depression mask. 15 are in this network. "in_nondep_net" refers to brain regios that completely avoided the depression network (i.e. had no shared volume of overlap). 40 are in this network.

@@

@@

    *Age effects:
      -Age mean 47 (range 20-83). 
      -Almost everything corrects (54 out of 87 fascicles, 25 in association network)
      -Take home - as expected, the older you are, the worse white matter fascicle invovlement you have

    *Sex effects:
      - In the final good MIMoSA group, there were 64 unique males and 316 unique females, 83% women
      - Individual fascicle results underwhelming, only 3 regions meet P<0.05 (unc), SCP, CPT_O_R, OR_R
      - no association or within dep network findings
      - Sex effects interaction model (fascicle ~ depGroupVar*osex + PAT_AGE_AT_EXAM)
        - Dep effects - same as above, 12 fascicles (p<0.05 unc)
        - Sex effects - same as above, with the edition of CNVIII_R (p<0.05 unc)
        - age*sex interactions - SLF1_L and CNVIII_R (p<0.05 unc)
      - Analyses to consider at a later date
        [] some sort of matching

    *Depression over all fascicles:
      - The exciting news of the day! With our new depression group (moving the meds people), we have findings
      - total proportion lost - p = 0.049, depressed (27%) more loss than healthy(24%)
      - total proportion lost within depression network (47 total) - trend (0.059) between depressed (35%) and healthy(30%)
      - total proportion lost within depression 10% network (15 fascicles total) - p = 0.049 (depressed (33%) have more loss than healthy (27%))
      - total proportion lost within depression 5% network (24 fascicles total) -  p = 0.056 (depressed (32%) have more loss than healthy (27%))
      - total proportion lost outside depression network (40 fascicles total)- p = 0.037 (depressed (18%) more than healthy(16%))
      - take home - people with a lifetime history of depression have more disease than nondepressed individuals. This finding is not specific to the depression network, but is overall.

    *MS disease and depression network overlap:
      - Ms disease within depression network (35%) versus outside (17%), p < 2.2* 10^-16
      - MS disease within depression 10% network (31%) versus outside (17%), p < 2.2 * 10^-16
      - MS disease within depression 5% network (30%) versus outside (17%), p < 2.2 * 10^-16
      - Linear Regressions (essentially matching t tests above): 
         +depressed v healthy within dep network in (p = 0.061); 
         +dep vs healthy within dep 10% (p = 0.049);
         +dep vs healthy within non dep network (p = 0.037)
      - Take home: Multiple sclerosis white matter lesions co-locate with brain regions previously associated with depression, irrespective of diagnosis. Suggests a final possible common pathway? Shared biology? This may also in part explain why rates of depression in MS are much higher than rates of depression in other autoimmune conditions. 
    *Depression by individual fascicle:
      - Nothing corrects at this time, unfortunately. 
      - P<0.05, uncorrected findings (* indicates association network):
          -AF_R	0.01168289	*		
          -FAT_R	0.01828607 *			
          -SLF2_R	0.01901378 *		
          -VOF_R	0.04741569 *			
          -CPT_F_R	0.02887163 			
          -CPT_O_L	0.02238344			
          -CPT_P_R	0.02053104			
          -CS_S_R	0.03783654			
          -DRTT_R	0.00695066			
          -ML_R	0.02511932	
    Fascicle loss x PHQ9:
     - Nothing significant by individual fascicle, within association network, by fascicle within the depression network
     - similarly, no significant findings looks at means of all fascicle loss, within dep network, 10% and 5% and non-depression network

Limitations/Future directions

  All diagnostic info is obtained from EMR fields, not notes, nor direct chart review. We do not know if patients are relapsing/remiting, nor do we know their active depression status. Through careful review, though patients sometimes have many phq2s listed, they are always identical. It is also possible that people who are on antidepressants are prescribed them not for depression. I tried a sensitivity analysis and removed people on meds from heatlhy group but didn't include them in the depression group. Unique n in depression group went from 232->115 and all findings go away.

  In order to do this, you need to change the mutate command:

##------
#goal is to keep people who were seen by

#### add this line #####
   mutate(dep_by_dx_phq_healthy_phq0_no_psych_meds = ifelse(dep_by_dx_phq | true_healthy, 1, 0)) %>%
   rowwise(ACCESSION_NUM) %>%

#### remove this line or comment out
    # mutate(depGroupVar = sum(c(dep_by_dx_phq_meds_healthy_phq0_no_psych_meds,dep_by_dx_phq))) %>%

#### add this line
   mutate(depGroupVar = sum(c(dep_by_dx_phq_healthy_phq0_no_psych_meds,dep_by_dx_phq))) %>%
   ungroup()
### -----

  It would be great if we also had better dimensional scores. The PHQ2s are largely 0s, and the lack of spread makes interpretation really challenging. Though the PHQ9s definitely have better spread, there just aren't many of them. Doing really good cognitive and clinical phenotyping, or even getting a different or better set of measures into the MS clinic would be ideal (Aim 2).

  With respect to networks, we have used the "depression" one from Harvard because I was inspired by the lesion network mapping work. However, the mask is pretty broad, covering and strongly overlapping with the executive network. There is bias toward having regions that functionally connect with the L DLPFC b/c it is a TMS target. We are considering neurosynth as a possible place to look at different depression masks.

  Interestingly, a key topic at the ACTRIMS 2022 conference was psychiatric comorbidity. Though we are focusing on depression, it sounds like anxiety is just as bad if not worse or more highly comorbid with MS. Would be worth considering not only a DSM breakdown but dimensionally looking at internalizing disorders for the K. Also more in line with rdoc but would require changing aims a bit.

  Future analyses: age x dep, sex x dep

@@

write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)

########
#fascicle volumes in depression network
########
fascicle_volumes_dep <- read.csv(paste0(homedir, "results/streamline_volume_within_dep_network.csv"), header = T, sep = ",")

#add column to indicate whether does not meet criteria for inclusion in dep mask (0), any overlapping voxels (1), or >10% overlapping voxels (2)
fascicle_volumes_dep_network <- fascicle_volumes_dep %>%
  replace(is.na(.), 0) %>%
  mutate(inDepMask=case_when(prop_in_mask == 0 ~ 0, (prop_in_mask > 0 & prop_in_mask < 0.1) ~ 1, prop_in_mask >= 0.1 ~ 2))

write.table(fascicle_volumes_dep_network, paste0(homedir,  "/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), sep = ",", col.names=T)#, row.names = F, quote = F, col.names = T)

fascicle_names_nondep_network<- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 0)]

fascicle_names_dep_network_all <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask > 0)]

@@

fascicle_names_dep_network_10_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 2)] #n=15
#write.table(fascicle_names_dep_network_10_percent,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_10_percent.csv", row.names = F, quote = F, col.names = F)

fascicle_names_dep_network_5_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$prop_in_mask >= 0.05)] #n=24

#fascicle_mapping, returns numerical mapping as well as names of tracts, and whether in or out of dep network
fascicle_bundle_mapping <- get_fascicle_bundle_mapping()

@@

######## Histograms for depression network
#this histogram helps contextualize the number of streamlines with varying degrees of proportions affected
hist(x=fascicle_volumes_dep$prop_in_mask, main = "Histogram Affected Streamlines in Dep Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20)

@@

#print(q)
#print(r)
print(r_color)
#print(x)
#print(y)
#print(z)
```

@@

#lm
fascicle_age_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

@@

@@

#lm
fascicle_sex_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$inDepNetwork_vector >0)]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

@@

#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_indepnet = rowMeans(across(fascicle_names_dep_network_all))) %>%
  mutate(total_fascicle_prop_lost_indepnet_10_percent =
           rowMeans(across(fascicle_names_dep_network_10_percent))) %>%
   mutate(total_fascicle_prop_lost_indepnet_5_percent =
           rowMeans(across(fascicle_names_dep_network_5_percent))) %>%
  mutate(total_fascicle_prop_lost_nondep_network =
           rowMeans(across(fascicle_names_nondep_network))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

@@

#power analysis to predict sample required for K, u = num df, v = denom df, f2=0.01 (cohen d = 0.02/2) 
#prop in each fascicle predicting dep (87), number of predictors (age, sex, ef, ess?) = 4, u = 87-4 = 83
pwr.f2.test(u=83, f2 = 0.02, sig.level = 0.5, power = 0.8)

@@

#look at within depression network specifically - trend, p = 0.059
total_volume_lost_dep_vs_healthy_unique_in_dep_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 36%, mean non_dep = 32%, p = 0.071

#look at within depression network in fascicles where at least 10% of the volume of the fascicle was in dep network
#yes, p = 0.048
total_volume_lost_dep_vs_healthy_unique_in_dep_network_10percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 33%, mean non_dep = 27%, p = 0.048

#look at within depression network in fascicles where at least 5% of the volume of the fascicle was in dep network
#yes, 
total_volume_lost_dep_vs_healthy_unique_in_dep_network_5percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_5_percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 32%, mean non_dep = 27%, p = 0.056

>>>>

---
title: "MS Yeo 7 Network Analyses"
author: "Erica Baller"
date: "6/28/2022"
output:
  pdf_document: default
  html_document: default
---

@@

## MS yeo network analyses

In doing my preliminary analyses for my K23, I became interested in how networks other than the depression network relate to MS. I specifically wondered about the classic yeo 7 networks, especially the frontoparietal network given previous depression literature as well as my own work. Furthermore, I have noticed that there are a lot of interesting sex differences, age differences, and depression differences all by fascicle, but they don't reach correction, suggesting that there might be benefit of dimensionality reduction. Thus, enter this new project.

The idea here is that I took the yeo volume map (the more liberal one: (**/Users/eballer/BBL/msdepression/templates/Yeo_JNeurophysiol11_MNI152/Yeo2011_7Networks_MNI152_FreeSurferConformed1mm_LiberalMask.nii.gz**), and separated it out into individual networks on my local machine (**/Users/eballer/BBL/msdepression/scripts/afni_commands_to_construct_yeo_indiv_vol_masks.sh**), and binarized them. I then moved them to pmacs and treated them as "lesions" to get the proportion of fascicle overlap with each of the 87 fascicles (**/project/msdepression/scripts/calc_vol_fascicles_within_yeo_7_net.sh**). The results, stored here (**/project/msdepression/results/yeo_7_network_overlap_proportions.txt**), go through each of 87 fascicles and identify the proportion of overlap of that fascicle's volume with each network. For example, if SLF2_L has a value of .27 in the FP network, it indicates that 27% of the fibers in the SLF2_L fascicle overlap in volume with the frontoparietal network volume mask. In the result (**/project/msdepression/results/yeo_7_network_overlap_proportions_binarized.txt**), results are binarized - if there is ANY overlap (i.e. if there is at least one voxel of overlap between the fascicle and the network, the value is 1, otherwise the value is 0). This method is cursory, I can also imagine a situation when I scale based on the proportion of overlap. It is also important to know that certain fibers overlap with multiple networks; this is NOT exclusionary. Certain fibers are more integrated. Many ways to go about thinking about this.

In the FIRST analysis here, I am just going to look at the frontoparietal network in the simplest condition - look at fascicles with a 1 in the FP column. The idea would be to look at overall effects, age effects, sex differences, depression diagnoses in fibers within and outside the FP network. I.e., comparing rows with a 1 for FP to a 0 for FP. Once I work this out, will repeat for other networks.

@@

  The networks are generated from the Yeo 7 networks (as above).

@@

FP Network (n = 54)
[1] "AF_L"    "AF_R"    "C_FPH_L" "C_FPH_R" "C_FP_L"  "C_FP_R"  "C_PHP_L" "C_PHP_R" "C_R_L"   "C_R_R"   "EMC_L"  
[12] "EMC_R"   "FAT_L"   "FAT_R"   "IFOF_L"  "IFOF_R"  "ILF_L"   "ILF_R"   "MdLF_L"  "PAT_L"   "PAT_R"   "SLF1_L" 
[23] "SLF1_R"  "SLF2_L"  "SLF2_R"  "SLF3_L"  "SLF3_R"  "UF_L"    "UF_R"    "CBT_L"   "CBT_R"   "CPT_F_L" "CPT_F_R"
[34] "CPT_P_L" "CPT_P_R" "CS_A_L"  "CS_A_R"  "CS_P_L"  "CS_P_R"  "CS_S_L"  "CS_S_R"  "CST_R"   "DRTT_L"  "DRTT_R" 
[45] "RST_L"   "RST_R"   "TR_A_L"  "TR_A_R"  "TR_P_L"  "TR_P_R"  "TR_S_L"  "TR_S_R"  "AC"      "CC"

NonFP Network(n=33)
 [1] "C_PH_L"   "C_PH_R"   "MdLF_R"   "VOF_L"    "VOF_R"    "CB_L"     "CB_R"     "ICP_L"    "ICP_R"    "MCP"     
[11] "SCP"      "V"        "CNIII_L"  "CNIII_R"  "CNII_L"   "CNII_R"   "CNVIII_L" "CNVIII_R" "CNVII_L"  "CNVII_R" 
[21] "CNV_L"    "CNV_R"    "AR_L"     "AR_R"     "CPT_O_L"  "CPT_O_R"  "CST_L"    "F_L"      "F_R"      "ML_L"    
[31] "ML_R"     "OR_L"     "OR_R"

FP_network_10percent (n = 16)
 [1] "AF_L"    "AF_R"    "C_FPH_R" "C_FP_R"  "C_PHP_R" "C_R_L"   "C_R_R"   "FAT_R"   "SLF2_L"  "SLF2_R"  "SLF3_R" 
[12] "CPT_F_R" "CS_A_L"  "RST_R"   "TR_A_L"  "TR_A_R"

nonFP_network_10percent (n = 71)
[1] "C_FPH_L"  "C_FP_L"   "C_PH_L"   "C_PHP_L"  "C_PH_R"   "EMC_L"    "EMC_R"    "FAT_L"    "IFOF_L"   "IFOF_R"  
[11] "ILF_L"    "ILF_R"    "MdLF_L"   "MdLF_R"   "PAT_L"    "PAT_R"    "SLF1_L"   "SLF1_R"   "SLF3_L"   "UF_L"    
[21] "UF_R"     "VOF_L"    "VOF_R"    "CB_L"     "CB_R"     "ICP_L"    "ICP_R"    "MCP"      "SCP"      "V"       
[31] "CNIII_L"  "CNIII_R"  "CNII_L"   "CNII_R"   "CNVIII_L" "CNVIII_R" "CNVII_L"  "CNVII_R"  "CNV_L"    "CNV_R"   
[41] "AR_L"     "AR_R"     "CBT_L"    "CBT_R"    "CPT_F_L"  "CPT_O_L"  "CPT_O_R"  "CPT_P_L"  "CPT_P_R"  "CS_A_R"  
[51] "CS_P_L"   "CS_P_R"   "CS_S_L"   "CS_S_R"   "CST_L"    "CST_R"    "DRTT_L"   "DRTT_R"   "F_L"      "F_R"     
[61] "ML_L"     "ML_R"     "OR_L"     "OR_R"     "RST_L"    "TR_P_L"   "TR_P_R"   "TR_S_L"   "TR_S_R"   "AC"      
[71] "CC"

@@

    *Age effects:
     FP network 54 fascicles, 48 correct
     Non fp network 33 fascicle, 7 correct
    *Sex effects:
     - no fdr corrected values

    *MS disease and FP network overlap:
    - w/in FP network by diagnosis, p = 0.63
    - w/in FP_10% by diagnosis, p = 0.64
    - nonFP, p = 0.27
    - non FP 10%, 0.49

    *Depression by individual FP fascicles:

    Fascicle loss x PHQ9:

@@

#write.table(fascicle_names,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names.csv", row.names = F, quote = F, col.names = F)

########
#fascicle volumes in yeo networks
########

#read in file with proportions
fascicle_volumes_yeo_7 <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions.txt"), header = T, sep = ",", na.strings="0")

#make titles nice
names(fascicle_volumes_yeo_7) <-gsub("prop_in_mask_", "prop_", names(fascicle_volumes_yeo_7))

#make Nas into 0
fascicle_volumes_yeo_7[is.na(fascicle_volumes_yeo_7)]=0

#read in file with binarized yes/no 
fascicle_volumes_yeo_7_binarized <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions_binarized.txt"), header = T, sep = ",")

#add column to indicate whether does not meet criteria for inclusion in dep mask (0), any overlapping voxels (1), or >10% overlapping voxels (2)
#fascicle_volumes_dep_network <- fascicle_volumes_dep %>%
 # replace(is.na(.), 0) %>%
#  mutate(inDepMask=case_when(prop_in_mask == 0 ~ 0, (prop_in_mask > 0 & prop_in_mask < 0.1) ~ 1, prop_in_mask >= 0.1 ~ 2))

#write.table(fascicle_volumes_dep_network, paste0(homedir,  "/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_grouping.csv"), sep = ",", col.names=T)#, row.names = F, quote = F, col.names = T)

fascicle_names_FP_network<- fascicle_volumes_yeo_7_binarized$fascicle[which(fascicle_volumes_yeo_7_binarized$FP == 1)]

fascicle_names_nonFP_network<- fascicle_volumes_yeo_7_binarized$fascicle[which(fascicle_volumes_yeo_7_binarized$FP == 0)]

fascicle_names_FP_network_10percent<- fascicle_volumes_yeo_7$fascicle[which(fascicle_volumes_yeo_7$prop_FP > 0.1)]

fascicle_names_nonFP_network_10percent<- fascicle_volumes_yeo_7$fascicle[which(fascicle_volumes_yeo_7$prop_FP <=0.1)]

@@

#fascicle_names_dep_network_10_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$inDepMask == 2)] #n=15
#write.table(fascicle_names_dep_network_10_percent,"/Users/eballer/BBL/msdepression/templates/dti/HCP_YA1065_tractography/fascicle_names_dep_network_10_percent.csv", row.names = F, quote = F, col.names = F)

#fascicle_names_dep_network_5_percent <- fascicle_volumes_dep_network$fascicle[which(fascicle_volumes_dep_network$prop_in_mask >= 0.05)] #n=24

#fascicle_mapping, returns numerical mapping as well as names of tracts, and whether in or out of dep network
#fascicle_bundle_mapping <- get_fascicle_bundle_mapping()

@@

######## Histograms for depression network

hist(x=fascicle_volumes_yeo_7$prop_VIS, main = "Histogram Affected Streamlines in VIS Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

hist(x=fascicle_volumes_yeo_7$prop_MOT, main = "Histogram Affected Streamlines in MOT Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

hist(x=fascicle_volumes_yeo_7$prop_DA, main = "Histogram Affected Streamlines in DA Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

hist(x=fascicle_volumes_yeo_7$prop_VA, main = "Histogram Affected Streamlines in VA Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

hist(x=fascicle_volumes_yeo_7$prop_LIM, main = "Histogram Affected Streamlines in LIM Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

hist(x=fascicle_volumes_yeo_7$prop_DM, main = "Histogram Affected Streamlines in DM Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

hist(x=fascicle_volumes_yeo_7$prop_FP, main = "Histogram Affected Streamlines in FP Net", xlab = "Proportion Streamlines per Fascicle Affected", breaks = 20, xlim=c(0,0.7), ylim=c(0,70))

#no breaks, trying to standardize visualization

hist(x=fascicle_volumes_yeo_7$prop_VIS, main = "Histogram Affected Streamlines in VIS Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))

hist(x=fascicle_volumes_yeo_7$prop_MOT, main = "Histogram Affected Streamlines in MOT Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))

hist(x=fascicle_volumes_yeo_7$prop_DA, main = "Histogram Affected Streamlines in DA Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))

hist(x=fascicle_volumes_yeo_7$prop_VA, main = "Histogram Affected Streamlines in VA Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))

hist(x=fascicle_volumes_yeo_7$prop_LIM, main = "Histogram Affected Streamlines in LIM Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))

hist(x=fascicle_volumes_yeo_7$prop_DM, main = "Histogram Affected Streamlines in DM Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))

hist(x=fascicle_volumes_yeo_7$prop_FP, main = "Histogram Affected Streamlines in FP Net", xlab = "Proportion Streamlines per Fascicle Affected", xlim=c(0,0.6), ylim=c(0,80))
```

@@

#print(q)
#print(r)
print(r_color)
#print(x)
#print(y)
#print(z)

### FP only; Just pull out FP data

#drop columns not in FP
just_fp_fascicles <- subset(x = fascicle_proportions, select = c("EMPI", "EXAM_DATE", fascicle_names_FP_network))

added_dep_to_fascicles <- merge(just_dep_and_empi, just_fp_fascicles, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

fp<-ggplot(lesioned, aes(x=value, fill=depGroupVar, color=factor(depGroupVar))) + geom_histogram() + facet_wrap(~variable)
print(fp)

#drop columns not in FP 10% 
just_fp_fascicles <- subset(x = fascicle_proportions, select = c("EMPI", "EXAM_DATE", fascicle_names_FP_network_10percent))

added_dep_to_fascicles <- merge(just_dep_and_empi, just_fp_fascicles, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

fp_10<-ggplot(lesioned, aes(x=value, fill=depGroupVar, color=factor(depGroupVar))) + geom_histogram() + facet_wrap(~variable)
print(fp_10)
######## Non FP networks
#drop columns in FP 
just_nonfp_fascicles <- subset(x = fascicle_proportions, select = c("EMPI", "EXAM_DATE", fascicle_names_nonFP_network))

added_dep_to_fascicles <- merge(just_dep_and_empi, just_nonfp_fascicles, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

nonfp<-ggplot(lesioned, aes(x=value, fill=depGroupVar, color=factor(depGroupVar))) + geom_histogram() + facet_wrap(~variable)
print(nonfp)

#drop columns in FP 10% 
just_nonfp_fascicles <- subset(x = fascicle_proportions, select = c("EMPI", "EXAM_DATE", fascicle_names_nonFP_network_10percent))

added_dep_to_fascicles <- merge(just_dep_and_empi, just_nonfp_fascicles, by = c("EMPI"))
melted_df <- melt(added_dep_to_fascicles, id.vars = c("EMPI", "EXAM_DATE", "depGroupVar"))

nonfp_10<-ggplot(lesioned, aes(x=value, fill=depGroupVar, color=factor(depGroupVar))) + geom_histogram() + facet_wrap(~variable)
print(nonfp_10)

@@

#lm fp
fascicle_age_lm <- lapply(fascicle_names_FP_network, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names_FP_network

@@

@@

#lm fp 10 %
fascicle_age_lm <- lapply(fascicle_names_FP_network_10percent, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names_FP_network_10percent

####### Non FP
#lm non fp 
fascicle_age_lm <- lapply(fascicle_names_nonFP_network, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names_nonFP_network

#visreg
#sapply(fascicle_age_lm,visreg)
#visreg(fascicle_age_lm$AF_R,ylab = "Proportion of Affected Streamlines", xlab = "Age in Years",
 #      line=list(col="red"),
  #     points=list(col="black"))

#lm nonfp 10 %
fascicle_age_lm <- lapply(fascicle_names_nonFP_network_10percent, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names_nonFP_network_10percent

#visreg
#sapply(fascicle_age_lm,visreg)
#visreg(fascicle_age_lm$AF_R,ylab = "Proportion of Affected Streamlines", xlab = "Age in Years",
 #      line=list(col="red"),
  #     points=list(col="black"))

@@

#lm fp
fascicle_sex_lm <- lapply(fascicle_names_FP_network, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names_FP_network

@@

#lm fp 10
fascicle_sex_lm <- lapply(fascicle_names_FP_network_10percent, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names_FP_network_10percent

####
#lm nonfp
fascicle_sex_lm <- lapply(fascicle_names_nonFP_network, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names_nonFP_network

#lm nonfp 10
fascicle_sex_lm <- lapply(fascicle_names_nonFP_network_10percent, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names_nonFP_network_10percent

@@

#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  mutate(total_fascicle_prop_lost_FP_network = 
           rowMeans(across(fascicle_names_FP_network))) %>%
  mutate(total_fascicle_prop_lost_FP_network_10percent =
           rowMeans(across(fascicle_names_FP_network_10percent))) %>%
  mutate(total_fascicle_prop_lost_nonFP_network =
           rowMeans(across(fascicle_names_nonFP_network))) %>%
  mutate(total_fascicle_prop_lost_nonFP_network_10percent =
           rowMeans(across(fascicle_names_nonFP_network_10percent))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

@@

@@

#look at fp network specifically - trend, p = 0.063
total_volume_lost_dep_vs_healthy_unique_in_FP_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_FP_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_FP_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #healthy = 28% dep = 32%

#look at within FP network in fascicles where at least 10% of the volume of the fascicle was in FP network
#yes, p = 0.064
total_volume_lost_dep_vs_healthy_unique_in_FP_network_10percent <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_FP_network_10percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_FP_network_10percent[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #healthy = 22% dep = 26%

#look at outside FPnetwork, yes p = 0.027
total_volume_lost_dep_vs_healthy_unique_in_nonFP_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nonFP_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nonFP_network[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #healthy = 17% dep = 20%
